---
title: "hw06-lh563"
author: "Lu Han"
date: "11/1/2018"
output: github_document
---

# Homework 06

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(MASS))

```

## Task 02
### Working with functions
First, let's filter the data of China
```{r}

(gap<- gapminder %>% 
  filter(country == "China"))
```

Plot the data.
```{r}
p <- ggplot(gap, aes(x = year, y = gdpPercap))
p + geom_point() + geom_smooth(method = "lm", se = FALSE)

```
Fit the linear regression model

```{r}
gap_lm <- lm(gdpPercap~year,data=gap)
coef(gap_lm)
```

From the previous graph, we can tell the linear regression is not a good model for the data as most of the dots do not fall on the line. From the coefficient, we can tell that when year=0, gdpPercap=intercept=-127509.31555 , which does not make sense. Hence, a quadratic regression model is applied to fit the data.
```{r}
gap_qm<- lm(gdpPercap~I(year)+I(year^2),data=gap)
coef(gap_qm)
```

The intercept is too large when the year=0. Hence, according to Jenny's tutorial, an offset of 1952 was applied.
```{r}
gap_qm2<- lm(gdpPercap~I(year-1952)+I(year^2-1952^2),data=gap)
coef(gap_qm2)
```

Create the function to do the coefficent automatically
```{r}
coef_function <- function(gap, offset=1952){
  gap_fit <-lm(gdpPercap~I(year-1952)+I(year^2-1952^2),data=gap)
  setNames(coef(gap_fit),c("intercept","year","year^2"))
}
coef_function(gap)
```
The values of intercept matches the previous coefficient values, suggesting the function created works.

Let's try with another country's data.
```{r}
(gap2 <- gapminder %>% 
  filter(country == "Australia"))
coef_function(gap2)

p2 <- ggplot(gap2, aes(x = year, y = gdpPercap))
p2 + geom_point() + geom_smooth(method = "lm", formula = y ~ x + I(x^2), se = FALSE)
```
The quadratic model fits the data well as we can see most of the dots fall on the line and the intercept is positive values not.

## Task 06
### Working with a nested dataframe
```{r}
#first, let's make a nested dataframe by grouping continent and country variable.
(nest_gapminder <- gapminder %>% 
  group_by(continent, country) %>% 
  nest())
```
```{r}
# Fit the data with a linear model and a robust model separately
linear_model <- function(data) {
  offset = 1952
  lm(lifeExp~I(year-1952),data)
}
#test the function with "afghanistan"
linear_model(nest_gapminder$data[[1]])

robust_model <-function(data) {
  offset = 1952
  MASS::rlm(lifeExp~I(year-1952),data)
}
#test the function with "afghanistan"
robust_model(nest_gapminder$data[[1]])
```

```{r}
(nest_gapminder_linear <- nest_gapminder %>% 
  mutate(fit_lm=map(data,linear_model),
         coefs_lm=map(fit_lm,tidy)) %>% #add two columns of fit_lm and coefs_lm
  select(continent, country, coefs_lm) %>% 
  unnest(coefs_lm))#unnest the coefs_lm column dataframe

(gapminderlm_ests <- nest_gapminder_linear %>% 
  select(continent:estimate) %>% 
  mutate(term=recode(term,
                     `(Intercept)`="Intercept",
                     `I(year-1952)`="slope")) %>% 
  spread(key=term,value=estimate))

```



```{r}

#Similar wrangling process to robust linear model
(nest_gapminder_robust <- nest_gapminder %>% 
  mutate(fit_rlm=map(data,robust_model),
         coefs_rlm = map(fit_rlm,tidy)) %>% 
  select(continent, country, coefs_rlm) %>% 
  unnest(coefs_rlm))

#Make the dataframe looks more handy by spreading the term and estimate
(gapminder_rlm_ests<-nest_gapminder_robust %>% 
    select(continent:estimate) %>% 
    mutate(term=recode(term,
                     `(Intercept)`="Intercept",
                     `I(year-1952)`="slope")) %>% 
  spread(key=term,value=estimate))
```

Now we can enjoy the payoff of the organized dataframe
```{r}
ggplot(nest_gapminder_linear, aes(estimate))+
         geom_density()+geom_rug()+facet_wrap(~term,scales = "free")
         
ggplot(nest_gapminder_robust, aes(estimate))+
         geom_density()+geom_rug()+facet_wrap(~term,scales = "free")
         
```
```{r}

```




